---
title: 'WST Pop Model: base model review'
output:
  html_document:
    df_print: paged
    toc: true
---

```{r setup, include=FALSE}

# knitr::opts_chunk$set(eval = FALSE)

# header ----
# Created: 12-Feb-2018
# Author:  J. DuBois
# Contact: jason.dubois@wildlife.ca.gov
# Purpose: this file contains code developed by S. Blackburn (Univ. of Idaho) &
#          're-coded' some by me (J. DuBois) in an effort to understand better & 
#          perhaps automate processes and methods used by S. Blackburn (SB)
# OrigR:   see 'WST_midfecund_obs_basemodel.txt' file

```

###Background
Most important, I want to understand how S. Blackburn (Univ. of Idaho; SB) took raw CDFW data, and then created dataframes (or other data types) to 'feed' the model. This is an important first-step towards understanding the model. Herein I explore how SB created the base model (15% spawning periodicity) and the various methodologies used to arrive at the final results (J. DuBois, 12-Feb-2018; see original SB file `WST_midfecund_obs_basemodel.txt`).

###Data
SB creates four data variables: `initial_age_dist`; `prob_survival_obs`; `prob_spawn`; and `number_eggs`. SB begins with a WST population abundance of 48000 (slot-sized?) from CDFW reports and Hildebrand et al. (2016). Below are these four data variables.

####Data: `initial_age_dist`
According to SB, these data are:  
1. Based on age-at-length key (NOT adjusted to trammel net selectivity) and scaled by initial_abundance (48000).   
2. Then used linear model with log-transformed count data (exponential decay fxn) to estimate age 1 and age 2 abundance. Then took 1/2 for females.  
3. Current age-0 abundance represents the number of eggs potentially in the system in a given year, which is based on number of spawning females and their associated fecundity.  

```{r age-dist}

# create variable (matrix with 20 rows & 2 columns)
initial_age_dist <- structure(
  c(
    # age
    0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10,
    11, 12, 13, 14, 15, 16, 17, 18, 19,
    # freq
    141491743, 3192.023, 2874.605,
    743.4951, 919.6688, 1887.2559, 2643.7050,
    3778.5699,4249.9032,3177.8537,1654.6577,
    1068.1057,597.0728,1214.5035,561.4314,858.8469,
    38.1710, 439.7614,148.104767, 148.1116858
  ),
  .Dim = c(20L, 2L),
  .Dimnames = list(NULL, c("age", "freq"))
)

```

####Data: `prob_survival_obs`
According to SB, these data are:  
1. Estimated from age-key, using Chapman-Robson peak plus one criterion and adjusted the SE for overdispersion (using chat variance inflation).  
2. Age age-0 and age-1 values are from literature.  
3. Conditional mortality, mortality in the absence of exploitation, was applied to fishes not in the harvest slot length limit.  

```{r prob-surv}

prob_survival_obs <- structure(
  list(
    # ages
    age = 0:19,
    # probabilities
    prob = c(
      0.002, 0.25, 0.835265413, 0.835265413,
      0.835265413, 0.835265413, 0.835265413,
      0.835265413, 0.835265413, 0.835265413,
      0.707049, 0.707049, 0.707049, 0.707049,
      0.707049, 0.707049, 0.835265413, 0.835265413,
      0.835265413, 0.835265413
    ),
    # standard error
    SE = c(
      0.003, 0.05, 0.0377, 0.0377, 0.0377,
      0.0377, 0.0377, 0.0377, 0.0377, 0.0377,
      0.01932, 0.01932, 0.01932, 0.01932,
      0.01932, 0.01932, 0.0377, 0.0377, 0.0377, 0.0377
    )
  ),
  .Names = c("age", "prob", "SE"),
  row.names = c(NA, -20L),
  class = "data.frame"
)

```

####Data: `prob_spawn`
According to SB, these data are:  
1. Estimated with logistic regression from Chapman et al. 1996 summarized data. First age of maturity for females was 10 years old (~104 cm; Chapman et al. 1996).  
2. SEs predicted from the logistic model.  

```{r prow-spawn}

prob_spawn <- structure(
  list(
    Age = c(
      0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10,
      11, 12, 13, 14, 15, 16, 17, 18, 19
    ),
    prob = c(
      0, 0, 0, 0, 0, 0, 0, 0, 0, 0,
      0.003726142, 0.01198, 0.021455, 0.046198, 0.078354,
      0.090394, 0.125679, 0.128829, 0.1419388, 0.144958
    ),
    SE = c(
      0, 0, 0, 0, 0, 0, 0, 0, 0, 0,
      0.00075, 0.00258, 0.00429, 0.00873,
      0.01629, 0.01866, 0.02364, 0.02547,
      0.02826,0.02898
    )
  ),
  .Names = c("Age", "prob", "SE"),
  row.names = c(NA, 20L),
  class = "data.frame"
)

```

####Data: `number_eggs`
According to SB, these data are:    
1. From the linear regression of length on number of eggs.   
2. SEs predicted from model.  

```{r number-eggs}

number_eggs <- structure(
  list(
    Age = c(
      0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10,
      11, 12, 13, 14, 15, 16, 17, 18, 19
    ),
    count = c(
      0, 0, 0, 0, 0, 0, 0, 0, 0, 0,
      33297.98, 87236.71, 112408.1, 141175.4,
      166346.9, 191518.3, 216689.7, 267032.4994,
      313779.4042, 335354.8988                     
    ),
    SE = c(
      0, 0, 0, 0, 0, 0, 0, 0, 0, 0,
      11069.74, 9886.758, 8626.421, 7640.275,
      6711.24, 6144.04, 5877.155, 5951.129,
      6354.067, 7029.626
    )
  ),
  .Names = c("Age", "count", "SE"),
  row.names = c(NA, 20L),
  class = "data.frame"
)

```

###Deterministic post-Breeding Matrix Model

According to SB:  
- This model does **NOT** include stochasticity (i.e., recruitment, vital rates)  
- Last age class does NOT die  

A post-breeding census means we capture newborns in our census, they are 1st age class  
- Row 1: how do we get new age-0 individuals in the next time step?  
- Animals we catch right AFTER (post) their birthday can contribute newborn (age 0) animals to next year's census by surviving to their next birthday, then reproducing ON that birthday.    
- Ex: fecundity of 9-year-olds (10th fecundity row element in matrix) is: survival from 9-10 (i.e., S9, 10th survival element), times fecundity on 10th bday (i.e., f10, 11th repro element)

```{r breeding-matrix}

# create breeding matrix
A <- matrix(
  data = rep(0, times = 19 *20),
  byrow = TRUE,
  nrow = 19
)

# f0-f19; 50% sex ratio
fecundity <- number_eggs$count[2:20] * prob_spawn$prob[2:20] * 0.5

# need to add f20, same as f19
fecundity <- c(fecundity, fecundity[19])							

row1 <- prob_survival_obs$prob * fecundity	

# Survival probablities of ages 0-19 
p.surv.obs = prob_survival_obs$prob[1:19]

# Manually add 19+ age class so that last age class does not die 
p.surv.obs.final = prob_survival_obs$prob[20]


diag(A) <- p.surv.obs

A[19, 20] <- p.surv.obs.final
A <- rbind(row1, A)

```

```{r get-lambda}

# Eigen values
ev <- eigen(A)    

# Absolute value of eigen values
Mod <- ev$values  

# Position of primary eigen value
lmax <- which.max(Re(ev$values)) 

# Primary eigen value 1.050753; does NOT include recruitment stochasicity
# (later)
Re(ev$values)[lmax]

# can also get lambda below
popbio::lambda(A)

```

```{r stabl-age-dist}

# Create stable age distribition (SAD) for easy comparasion to transient (i.e.,
# intitial_age_dist) dymanics

# SAD should be higher than transient dymanics because it negates
# cohort/year-class effects
SAD <- popbio::eigen.analysis(A)$stable.stage
stable_age_dist <- 10000 * SAD
stable_age_dist

```

####Practice Simulation
SB creates a practice simulation below. Mostly, it changes the number of iterations (see `iters` variable) for the function `pop.projection()` in the `popbio` package. To get a sense of what this function does, I demo it below SB's code.

```{r practice-sim}

# iteration variable
iters <- c(20, 100, 1000, 10000)

# variable to hold lambdas and CIs
my_lambdas <- c()
my_lambdas_CIs <- c()

for (i in 1:length(iters)) {
  determ_proj <- popbio::pop.projection(
    A = A,
    n = initial_age_dist[, 2], # column 2 is frequency
    iterations = iters[i]
  )
  
  my_log_lambdaS <- mean(log(determ_proj$pop.changes))
  
  # my note (15-Feb-2018): no log taken of determ_proj$pop.changes
  my_log_lambdaS_SE <- 1.96 * sqrt(var(determ_proj$pop.changes / iters[i]))
  
  my_log_lambdaS_CI <- c(
    my_log_lambdaS - my_log_lambdaS_SE,
    my_log_lambdaS + my_log_lambdaS_SE
  )
  
  my_lambdas <- c(my_lambdas, exp(my_log_lambdaS))
  my_lambdas_CIs <- rbind(my_lambdas_CIs, exp(my_log_lambdaS_CI))
}
# end for loop

mean(my_lambdas)

```

*Demo of `pop.projection()`*

```{r det-proj}

# uses 20 iterations for simplicity
det_proj <- popbio::pop.projection(
    A = A,
    # column 2 is frequency
    n = initial_age_dist[, 2],
    iterations = 20
  )

# det_proj is a list of 5 elements
# (1) lambda as pop[t] / pop[t - 1], where t = iterations, or the final
#     two values in pop.sizes
# (2) stable.stage: est. of stable stage distribution
# (3) stage.vector: matrix w/ # of projected individuals in each stage class
# (4) pop.sizes: total number of projected individuals
# (5) pop.changes: proportional change in population size

# not sure in this context I understand the purpose of taking log() 
det_proj$pop.changes
cat("\n")
log(det_proj$pop.changes)

```

###Stochastic Matrix Model

Here SB calculates stochastic log growth rate by simulation (an approach outlined pg. 234 Morris & Doak; same approach also used by Ng & Syslo in their respective theses).

The approach --- as SB writes --- has 7 main steps.  

1. Simulate Ai iid population matrices, i = 1:n, n is the number of simulations, where the random iid vital rates are drawn from the following distributions:  
    + i.  prob_survival ~ Beta(a, b) with a and b such that E(prob_survival) = mean, and Var(prob_survival) = SE^2  
    + ia. include recruitment stochasticity (i.e., age-0 survival)  
    + ii. prob_spawn ~ Beta(a, b) with a and b such that E(prob_spawn) = mean, and Var(prob_spawn) = SE^2  
    + iii. number_eggs ~ StretchBeta(a, b, min, max) with same type of expectation and variance as above.  support = [min, max] = [0, 2* maxobs] Use functions betaval() and stretchbetaval() to generate from Beta and StretchBeta distributions, respectively, with the appropriate parameters.  2. Assemble vital rates into post-breeding matrices which includes newborns (age-0) in the census as the 1st age class    
3. Use pop.projection() function to iterate each population j = 1:t times by multiplying matrix Ai by the population vector at time j. Because the same Ai will be used across the t times, we are interested when t is large (to look at long-term changes in the population)  
    + a. Calculate observed lambda for each matrix at time t by comparing the population change from time t-1 to time t (which is already done by pop.proj in pop.changes)  
4. Calculate the mean log lambda for each Ai  
5. For the overall value, look at the geometric mean of the lambdas.  
6. Evaluate sensitivity and elasticity values  
7. Look at how lambda changes over time

Let's look at each step...

####Step 1: simulate `iid` vital rates

#####Observed Survival Rates
In `prob_survival_obs` we have observed survival rates and standard deviations (assuming `SE` is standard deviation; see 'Questions' section).

```{r sim-surv_rates}

# establish variable with number of iterations; SB we set iters to 5000 for
# final runs of model; my note: writes over previously established iters
# variable
iters <- 100

# establish variable to hold for loop results
surv_obs_sims <- c()

# create for loop to run through each row of prob_survival_obs
for (i in 1:20) {
  age_sims <- replicate(
    n = iters,
    expr = popbio::betaval(
      # observed survival rates
      mn = prob_survival_obs[i, 2],
      # standard deviations (or standard errors?)
      sdev = prob_survival_obs[i, 3]
    )
  )
  
  surv_obs_sims <- rbind(surv_obs_sims, age_sims)
}
# end for loop

# not displayed due to size (large matrix) - where row = age & column =
# simulations
dim(surv_obs_sims)

```

Here SB "simulates environmental stochasticity for age-0 survival only. WST only having successful recruitment every 5 years (on average)."

DuBois<a id="c1"></a>: Is simulation on age-0 only for recruitment purposes?  
DuBois<a id="c2"></a>: Successful recruitment every 5 or 7 years (on average)? Not clear from annotations.

<a href="#quest">return to questions</a>

```{r sim-stoch}

# isolate age-0 simulated survival 
recruit_rate <- surv_obs_sims[1, ]

# on avg. successful recruitent every 7 years; recruit_dat now has 700 values
recruit_dat <- c(rep(0, times = iters * 6), recruit_rate)

# randomnly sample from recruit_dat; sample size = number of iterations
V <- sample(recruit_dat, size = iters, replace = TRUE)            

# replace age-0 simulated survival rates 
surv_obs_sims[1, ] <- V                             

# check to make sure new vector was succesfully added 
# not run due to size
# head(surv_obs_sims) 

# just FIO
# typeof(recruit_dat)
# str(recruit_dat)
# surv_obs_sims[1, ]

```

Check the simulations against the observed values in `prob_survival_obs`.

```{r sims-check_surv}

surv_obs_check <- cbind(
  prob_survival_obs,
  sim_prob = round(apply(surv_obs_sims, MARGIN = 1, FUN = mean), digits = 4),
  sim_SE = round(apply(surv_obs_sims, MARGIN = 1, FUN = sd), digits = 4)
) 

# view to ensure 20 ages classes (0 --> 19) are present; ages 20+ will be added
# later in the process
surv_obs_check

# just FIO
# plot(prob ~ sim_prob, data = surv_obs_check)

```

#####Probability of Spawning
Here we repeat the process above except using `prob_spawn` instead of `prob_survival_obs`.

```{r sim-prop_spawn}

prob_spawn_sim <- c()

# loop through each row (or age class)
for (i in 1:20) {
  spawn_sims <- replicate(
    n = iters,
    expr = popbio::betaval(
      # probability of spawning
      mn = prob_spawn[i, 2],
      # standard deviation
      sdev = prob_spawn[i, 3]
    )
  )
  
  prob_spawn_sim <- rbind(prob_spawn_sim, spawn_sims)
}
# end for loop

# result is matrix num of rows = age classes, num of columns = iters
dim(prob_spawn_sim)

```

Again, we check simulated against observed.

```{r sims-check_spawn}

prob_spawn_check <- cbind(
  prob_spawn,
  sim_prob = round(apply(prob_spawn_sim, MARGIN = 1, FUN = mean), digits = 4),
  sim_SE = round(apply(prob_spawn_sim, MARGIN = 1, FUN = sd), digits = 4)
)

# display dataframe
prob_spawn_check

```

#####Number of Eggs
Using data in `num_eggs` simulate number of eggs, again with `for()` loop but this time using `popbio::stretchbetaval()`.

```{r sim-num_eggs}

# variable to hold simulations
num_eggs_sim <- c()

# loop through rows (that is ages)
for (i in 1:20) {
  eggs_sims <- replicate(
    n = iters,
    expr = popbio::stretchbetaval(
      # count
      mn = number_eggs[i, 2],
      # standard deviation
      std = number_eggs[i, 3],
      minb = 0,
      maxb = 3 * number_eggs[i, 2],
      fx = runif(1)
    )
  )
  
  num_eggs_sim <- rbind(num_eggs_sim, eggs_sims)
}

# check for 20 x 100
dim(num_eggs_sim)

```

Check the simulations

```{r sim-check_eggs}

num_eggs_check <- cbind(
  round(number_eggs, digits = 4),
  sim_num = round(apply(num_eggs_sim, MARGIN = 1, FUN = mean), digits = 4),
  sim_SE = round(apply(num_eggs_sim, MARGIN = 1, FUN = sd), digits = 4)
) 

num_eggs_check

```

#####Fecundity
Simulate fecundity rate from `prob_spawning_sims` & `number_eggs_sims`

```{r}

# assumes 50% sex ratio
fecund_sim <- num_eggs_sim * prob_spawn_sim * 0.5

# check to make sure fecundity look right - should be 20 x 100
# tail(fecund_sim) 
dim(fecund_sim)

```

####Step 2: make random projection matrices
Here SB creates post-breeding Leslie matrices, which include WST caught right **AFTER** (post) their "birthday" (i.e., Jan 1)

DuBois<a id="c3"></a>: Is "caught" referring to in CDFW trammel nets, or by anglers or both? Or something else?

<a href="#quest">return to questions</a>

```{r proj-matrices}

random_matrices <- list()

for (i in 1:iters) {
  
  # 20 columns by 19 rows; will add top extra row (fecundity)
  A <- matrix(data = rep(0, times = 19 * 20), byrow = TRUE, nrow = 19)
  
  # for simplicity A can be
  # A <- matrix(data = 0, nrow = 19, ncol = 20)
  
  # survival rates age 0 through 19
  diag(A) <- surv_obs_sims[1:19, i]
  
  # last age class does NOT die
  A[19, 20] <- popbio::betaval(
    mn = prob_survival_obs[20, 2],
    sdev = prob_survival_obs[20, 3]  )
  
  # add new element to list
  random_matrices[[i]] <- as.matrix(
    rbind(fecund_sim[, i] * surv_obs_sims[, i], A)
  )
}
# end for loop

# make sure structure looks right 
# head(random_matrices)

# random_matrices s/b list w/ 100 elements each element is 20x20 matrix

# run FIO
# length(random_matrices)
# Map(f = dim, random_matrices)


```

####Step 3: Apply function `popbio::pop.projection()`

For each element in `random_matrices` (n=`r length(random_matrices)`) apply `popbio::pop.projection()`.

DuBois<a id="c4"></a>: Should column 2 (`freq`) be selected for `initial_age_dist` below?

<a href="#quest">return to questions</a>

```{r pop-projection}

# set number of years over which to perform projection
period <- 20

sim_projections <- lapply(
  seq_along(random_matrices),
  FUN = function(i) {
    popbio::pop.projection(
      A = random_matrices[[i]],
      n = initial_age_dist,
      iterations = period
    )
  }
)

# for simplicity sim_projections can be this
# sim_projections <- lapply(
#   random_matrices,
#   FUN = popbio::pop.projection,
#   n = initial_age_dist,
#   iterations = period
# )

```

####Step 4: Calculate mean log lambdas

For each element in `sim_projections`, get the average log-lambda to look at "sampling distribution" of the log lambdas.

SB notes an aside that Cox calculated mean of *theoretical* lambdas. But SB says not to use these in final analysis. See SB's `.txt` file for code.

DuBois<a id="c5"></a>: Why apply log in this manner?

<a href="#quest">return to questions</a>

```{r log-lambda}

# just the lambdas
log_lambdaS <- sapply(seq_along(sim_projections), FUN = function(i) {
  mean(log(sim_projections[[i]]$pop.changes))
})

# for simplicity log_lambdaS can be this
# log_lambdaS <- vapply(
#   sim_projections,
#   FUN = function(x) mean(log(x[["pop.changes"]])),
#   FUN.VALUE = numeric(1L)
# )

mean(log_lambdaS)

```

####Step 5: Calculate geometric mean of lambdas

Geometric mean is just the mean of the log lambdas, exponentiated.

DuBois<a id="c6"></a>: `exp` and then `mean` OR `mean` then `exp`? 

<a href="#quest">return to questions</a>

```{r geom-mean_lambdas}

mean_lambdaS <- exp(mean(log_lambdaS))

# Presumably we can find the 95% CIs in the same way:
LB_lambdaS <- exp(quantile(log_lambdaS, probs = 0.025))
UB_lambdaS <- exp(quantile(log_lambdaS, probs = 0.975))

c(LB_lambdaS, Mean = mean_lambdaS, UB_lambdaS)

```

####Step 6: sensitivity & elasticity analysis
DuBois (note-to-self): need to look at help file for `popbio::stoch.sens()`.

This gets at the elasticity - what vital rate has greatest influece over pop rate.

```{r sens}

sens <- popbio::stoch.sens(A = random_matrices, tlimit = 100)

# big list
# sens

names(sens)
str(sens)

```

####Step 7: lambdas over time

`sim_projections` is a list with `r length(sim_projections)` elements. Each item contains `r length(sim_projections[[1]])` items. We want the `pop.changes` (lambda, $\lambda$) item from each element.

DuBois<a id="c7"></a>: The x-axis is labeled as 'Year' but should be 'Age' in this context, correct? Or maybe it refers to year of fishes life? For instance, `1` is first year of sturgeon's life.

<a href="#quest">return to questions</a>

```{r plot-lambdas}

# herein I simplified a bit of the code & used ggplot (J. DuBois)

library(ggplot2)

# combine 100 pop.changes outputs to matrix for convenience of plotting
lambdas_time <- do.call(
  what = rbind,
  args = Map(f = function(x) x[["pop.changes"]], sim_projections)
)

ggplot(
  data = reshape::melt.matrix(data = lambdas_time),
  mapping = aes(x = X2, y = value)
) +
  geom_line(mapping = aes(group = X1), alpha = 1/10) +
  labs(x = "Year", y = "Lambda")

```

Not sure I understand SB's code below. `lambdas.time` has `r dim(lambdas_time)[1]` rows & only `r dim(lambdas_time)[2]` columns. So `40:ncol(lambdas.time)` will error as subscript out-of-bounds. Should the matrix be reversed? Note: typo in references to `MeanLambdas5`, should be `MeanLambdas15`, I believe.

```{r sb-code, eval=FALSE}

# not evaluated

## Take the lambdas from year 2 on ##
lambdas2 <-lambdas.time[,2:ncol(lambdas.time)]

# Geometric mean for each iteration from year 2 on...
MeanLambdas2 <-c()
for(i in 1:nrow(lambdas2)){
  MeanLambdas2[i]<-exp(mean(log(lambdas2[i,])))
}
mean(MeanLambdas2)

## Take the lambdas from year 15 on ##
lambdas15 <-lambdas.time[,15:ncol(lambdas.time)]

# Geometric mean for each iteration from year 15 on...
MeanLambdas15 <-c()
for(i in 1:nrow(lambdas15)){
  MeanLambdas5[i]<-exp(mean(log(lambdas5[i,])))
}
mean(MeanLambdas15)

## Now take the lambdas from year 40 on ##
lambdas40 <-lambdas.time[,40:ncol(lambdas.time)]

# Geometric mean for each iteration from year 40 on...
MeanLambdas40 <-c()
for(i in 1:nrow(lambdas40)){r
  MeanLambdas40[i]<-exp(mean(log(lambdas40[i,])))
}
mean(MeanLambdas40)

```

###Questions<a id="quest"></a>

**female spawing once ever 6 years; THIS FILE NOT CORRECTED FOR GEAR SELECTIVITY**

Click on "context" (when available) to see question within section (context) of document.

1. Can all initial (starting) data be class `data.frame`? `initial_age_dist` is a matrix.  
   *correct*
2. Are we assuming a 50% sex ratio?  
   *correct; just stuck with this throughout modeling*
3. Variable `A` is a Leslie Matrix, yes? 
   *yes*
4. For the practice simulation of the deterministic model, why is it necessary to take the log of the `pop.changes` vector?  
   *gets lambda, eigen values*
5. Some very large values in `determ_proj$pop.sizes`. Any explanation?  
   *artifact of starting population*
6. Is simulation on age-0 only for recruitment purposes? <a href="#c1">context</a>   
   *model pre & post breeding census; pre don't need to have age0 included; mostly for stochastic model*
7. Successful recruitment every 5 or 7 years (on average)? Not clear from annotations. <a href="#c2">context</a> 
   *every 6 years, but she changed to 8 years*
8. Is "caught" referring to in CDFW trammel nets, or by anglers or both? Or something else? <a href="#c3">context</a>  
   *refers to catching (sampling) newborns after Jan 1st*
9. Should column 2 (`freq`) be selected for `initial_age_dist`? <a href="#c4">context</a>  
   *could be but needs more investigation*
10. Why apply log in this manner? <a href="#c5">context</a>
    *to get geometric mean*
11. `exp` and then `mean` OR `mean` then `exp`?  <a href="#c6">context</a> 
   *apply mean and then exp*
12. The x-axis is labeled as 'Year' but should be 'Age' in this context, correct? Or maybe it refers to year of fishes life? For instance, `1` is first year of sturgeon's life. <a href="#c7">context</a>  
  *discarded this figure*

<a href="#top">return to top</a>

----
ran: `r Sys.time()`  
CDFW, Sportfish unit