---
title: "WST Pop Model: von Bertalanffy Growth Model (VBGM)"
output:
   html_document:
     df_print: paged
     toc: true
   html_notebook: default
---

```{r setup, include=FALSE}

# knitr::opts_chunk$set()
knitr::opts_knit$set(root.dir = "~/Rprojects/SturgeonPopModel/")

# ----
# Created: 09-Feb-2018
# Author:  J. DuBois
# Contact: jason.dubois@wildlife.ca.gov
# Purpose: this file contains code developed by S. Blackburn (Univ. of Idaho) &
#          're-coded' some by me (J. DuBois) in an effort to understand better & 
#          perhaps automate processes and methods used by S. Blackburn (SB)
# OrigR:   see 'VBGM.txt' file

```

###Background
Most important, I want to understand how S. Blackburn (Univ. of Idaho; SB) took raw CDFW data, and then created dataframes (or other data types) to 'feed' the model. This is an important first-step towards understanding the model. Herein I explore how SB used von Bertalanffy growth models (VBGM) in the model (J. DuBois, 09-Feb-2018; see original SB file `VBGM.txt`).

###Data
SB loads Excel file `BCLA.xlsx`, which contains fork length (fl) and age data fields. SB assigns loaded data to variable `wst`. (I saved this file as `.csv` for convenience of loading.)

```{r load-data}

wst <- read.csv(file = "blackburn_code/BCLA.csv", header = TRUE)
summary(wst)

```

Simply, SB plots fork length as a function of age to examine length-at-age.

```{r plot-len_age}

# formatting from SB not included here
plot(fl ~ age, data = wst)

```

###Create VB growth function
Using `vbFuns()` in package `FSA`, SB creates a 'typical' von Bertalanffy growth function.

```{r vb-fun, eval=TRUE}

vb <- FSA::vbFuns(param = "Typical", msg = TRUE)
vb

```

Generate starting values for VBGM using `vbStarts()`.

```{r vb-starts}

# automatic methods
wst_vbs <- FSA::vbStarts(
  fl ~ age,
  data = wst,
  type = "Typical",
  plot = TRUE
)

# ... or manual method
wst_vbs <- FSA::vbStarts(
  fl ~ age,
  data = wst,
  type = "Typical",
  plot = TRUE,
  fixed = list(Linf = 160, K = 0.3, t0 = 0)
)

```

###Fit VBGM to data
Using `nls()` and `vb()` fit growth model to data.

```{r fit-vbgm}

wst_vbf <- stats::nls(
  fl ~ vb(t = age, Linf = Linf, K = K, t0 = t0),
  data = wst,
  start = wst_vbs
)

# look at residual plot
FSA::residPlot(wst_vbf)

# extract results
summary(wst_vbf)

summary(wst_vbf, correlation = TRUE)
wst_vbc <- coef(wst_vbf)
cbind(Est = wst_vbc, confint(wst_vbf))

```

###Bootstrap estimates of uncertainty
Using `nlsBoot()` from `nlstools` package, get confidence intervals.

```{r boot-strap}

wst_vbb <- nlstools::nlsBoot(wst_vbf, niter = 1000)

str(wst_vbb)
FSA::headtail(wst_vbb$coefboot)
cbind(EST = wst_vbc, confint(wst_vbb, plot = TRUE, rows = 1, cols = 3))

```

####Predictions

So the results below are saying a White Sturgeon age 9 has a fork length of 101.5 with 95% CI of 100.95 to 102.07, yes?

```{r pred-vbb}

ageX <- 9
predict(wst_vbf, newdata = data.frame(age = ageX))

wst_vbbp <- apply(wst_vbb$coefboot, MARGIN = 1, FUN = vb, t = ageX)

c(
  pred = predict(wst_vbf, data.frame(age = ageX)),
  quantile(wst_vbbp, probs = c(0.025, 0.975))
)

```

not quite sure what's going on in this section lines 74:86 but I think SB is adding some CIs to the predictions.

SB is plotting fl ~ age and then adds predicted curve (I think)

```{r plot-pred}

clrs <- FSA::col2rgbt(col = c("black", "blue"), transp = 5/20)

# plot fl ~ age with curve added
plot(
  formula = fl ~ age,
  data = wst,
  pch = 19,
  col = clrs[1]
)
curve(
  vb(t = x, wst_vbc),
  from = 1, to = 30, n = 500,
  lwd = 2,
  col = clrs[2],
  add = TRUE
)

# predict length from ages 1 to 50 years
nd <- c(1:50)
predict(wst_vbf, data.frame(age = nd))

# plot(x = nd, y = predict(wst_vbf, data.frame(age = nd)))

```

###Questions
1. From where did the data in `BCLA.xlsx` come?  
   *374 fish from CDFW plus back calculated, used to back calculate young and old fish*
2. Parameters from this VBGM are used in the exploitation rate ($\mu$) estimation, correct? If so, which final `Linf`, `K`, and `t0` were used?  
   *yes, correct, Linf = 380, k = 0.027, t0 = -2.3*
3. In the manual method, were `Linf = 160`, `K = 0.3`, `t0 = 0` exploratory? Or did these values come from literature or an output?  *just exploratory*

Below is me noodling...

```{r noodling, eval=TRUE}

library(ggplot2)

# me noodling 14-Feb-2018
test <- lapply(1:1000, FUN = function(i) {
  len <- vb(
    t = 1:50,
    Linf = wst_vbb$coefboot[i, "Linf"],
    K = wst_vbb$coefboot[i, "K"],
    t0 = wst_vbb$coefboot[i, "t0"]
  )
  
  # output
  data.frame(
    age = 1:50,
    fl = len,
    group = as.character(i)
  )
})

ggplot(
  data = do.call(what = rbind, args = test),
  mapping = aes(x = age, y = fl, group = group)
) +
  geom_line(alpha = 1/10, linetype = 2, colour = "steelblue")

```

<a href="#top">return to top</a>

----
ran: `r Sys.time()`  
CDFW, Sportfish unit  
